Causal inference is not a statistical problem

### 2023-04-14 manuscript.qmd
re-render and modify code to fit in frame

## Table 2

causal_quartet |>
  nest_by(dataset) |>
  mutate(`ATE not adjusting for Z` = round(coef(lm(outcome ~ exposure, data = data))[2], 2),
         `ATE adjusting for Z` = round(coef(lm(outcome ~ exposure + covariate, data = data))[2], 2),
         `Correlation of X and Z` = round(cor(data$exposure, data$covariate), 2)) |>
  select(-data, dataset) |>
  knitr::kable("latex", 
               booktabs = TRUE,
               escape = FALSE, 
               col.names = 
                 kableExtra::linebreak(c("Data generating mechanism", 
                                         "ATE\nnot adjusting for Z", 
                                         "ATE\nadjusting for Z", 
                                         "Correlation of\nX and Z"), align = "c")) 
```

@@

causal_quartet_time |>
  nest_by(dataset) |>
  mutate(`ATE not adjusting for Z` = round(coef(lm(outcome_followup ~ exposure_baseline, data = data))[2], 2),
         `ATE adjusting for Z` = round(coef(lm(outcome_followup ~ exposure_baseline + covariate_baseline, data = data))[2], 2)) |>
  bind_cols(tibble(truth = c(1, 0.5, 1, 1))) |>
  select(-data, dataset) |>
  knitr::kable("latex", 
               booktabs = TRUE,
               escape = FALSE, 
               col.names = 
                 kableExtra::linebreak(c("Data generating mechanism", 
                                         "ATE\nnot adjusting for\npre-exposure Z", 
                                         "ATE\nadjusting for\npre-exposure Z",
                                         "Correct causal effect"), align = "c"),
               digits = 2) 
```

>>>>

## Table 2
round_coefs <- function(.mdl) {
  round(coef(.mdl)[2], 2)
}

causal_quartet |>
  nest_by(dataset) |>
  mutate(
    `ATE not adjusting for Z` = round_coefs(lm(outcome ~ exposure, data = data)),
    `ATE adjusting for Z` = round_coefs(lm(outcome ~ exposure + covariate, data = data)),
    `Correlation of X and Z` = round(cor(data$exposure, data$covariate), 2)
  ) |>
  select(-data, dataset) |>
  knitr::kable(
    "latex", 
    booktabs = TRUE,
    escape = FALSE, 
    col.names = kableExtra::linebreak(c(
      "Data generating mechanism", 
      "ATE\nnot adjusting for Z", 
      "ATE\nadjusting for Z", 
      "Correlation of\nX and Z"
      ), align = "c")
  ) 
```

@@

causal_quartet_time |>
  nest_by(dataset) |>
  mutate(
    `ATE not adjusting for Z` = 
      round_coefs(lm(outcome_followup ~ exposure_baseline, data = data)),
    `ATE adjusting for Z` = 
      round_coefs(lm(
        outcome_followup ~ exposure_baseline + covariate_baseline, 
        data = data
      ))
  ) |>
  bind_cols(tibble(truth = c(1, 0.5, 1, 1))) |>
  select(-data, dataset) |>
  knitr::kable(
    "latex", 
    booktabs = TRUE,
    escape = FALSE, 
    col.names = kableExtra::linebreak(c(
      "Data generating mechanism", 
      "ATE\nnot adjusting for\npre-exposure Z", 
      "ATE\nadjusting for\npre-exposure Z",
      "Correct causal effect"), align = "c"),
    digits = 2
  ) 
```
